Visualization and analysis of probability distributions of large temporal data

### 2021-11-17 Rmd/05-conclusion.Rmd
conclusion proofread

### Computational resources
Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches in \@ref(ch-hakear). In \@ref(ch-gracsr), our methods were tested on several data designs with different parameters to evaluate their performance. $wpd$ is computationally heavy for cyclic granularities with smaller levels. Moreover, JS and WPD approaches are also computationally intensive when run on large number of customers. Hence, most of the scripts used to run these studies use parallel processing for better computational speed. R version 4.0.1 (2020-06-06) is utilized on the platform x86 64-apple-darwin17.0 (64-bit) operating on macOS Mojave 10.14.6, as well as the High Performance Computing (HPC) resources provided by [MonARCH](https://docs.monarch.erc.monash.edu/MonARCH/aboutMonArch.html).

>>>>

### Computational resources
Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches in Chapter \@ref(ch-hakear). In Chapter \@ref(ch-gracsr), our methods were tested on several data designs with different parameters to evaluate their performance. $wpd$ is computationally heavy for cyclic granularities with smaller levels. JS and WPD approaches are also computationally intensive when run on large number of customers. Hence, most of the scripts used to run these studies use parallel processing for better computational speed. R version 4.0.1 (2020-06-06) is utilized on the platform x86 64-apple-darwin17.0 (64-bit) operating on macOS Mojave 10.14.6, as well as the High Performance Computing (HPC) resources provided by [MonARCH](https://docs.monarch.erc.monash.edu/MonARCH/aboutMonArch.html).
